---
title: "Fishing Strategy Randomization"
author: "Jonathan E. Falciani^[Temple University, Gulf of Maine Research Institute, jonathan.e.falciani@gmail.com]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    theme: cerulean
    toc: TRUE
    toc_depth: 3
  pdf_document:
    toc: TRUE
    toc_depth: 3
---

# Aim and Scope

Here we develop the code that generates the data we want to analyze. We will create a fish community consisting of 9 species that each differ by their asymptotic weight $W_\infty$. These 9 species will be divided into 3 different classes:

  * 3 *small* species ($W_\infty < 100$g),
  * 3 *medium* species ($100$g $< W_\infty < 1.5$kg), and
  * 3 *large* species ($1.5$kg $< W_\infty$).
  
Each of the 3 classes will be harvested on a species-specific basis, however each species within a class will share the same harvesting parameters $S$ and $F$. Each species will be selected by a knife-edge selectivity function harvesting all fish at or above a proportion of $W_\infty$, called *selectivity* $S$ ($0 < S < 1$). The selected fish of each species will be fished at a *fishing mortality* $F$ ($0 < F < 3$). Since $S$ and $F$ are shared by the species within a class, there are 6 independent variables. Each of these 6 variables will be uniformly sampled from their predesignated ranges shown above.

  * $S_{S}$ and $F_{S}$
  * $S_{M}$ and $F_{M}$
  * $S_{L}$ and $F_{L}$.
  
Each run will allow the simulation to run for 300 years to guarantee it reaches a steady state. Each run will collect information on biomass $B$, yield $Y$, extirpations $E$, biomass flux $B_{flux}$, and average size $W_{avg}$.

First we need to load in the `mizer` [package](https://sizespectrum.org/mizer).

```{r project pkg, message=FALSE, warning=TRUE}
library(mizer)
```

Run `devtools::load_all` in order to load all of the necessary functions inside the `fishcarbon` R project. If you are not, then see the functions vignette for the functions needed.

```{r project functions, eval=TRUE, message=FALSE, warning=FALSE}
devtools::load_all("./", export_all = TRUE)
```

The other R packages needed are:

```{r required packages, message = FALSE}
library(tidyverse)
library(here)
```


$~$
# Simulations

Each strategy will be given a unique `stratID`. Since we aim to generate upwards of 10,000 strategies which each take ~30 seconds to run, we will chunk this code into parts where we only generate a small subset of the 10,000 strategies as defined by `counter`. This will be added to the `fishcarbon_metrics.csv` file everytime it is run.

```{r read prior strats}
strategies_df <- read.csv(file.path(here(), 'data',
                                    'fishcarbon_metrics.csv'),header = TRUE)
```


## Unharvested Simulation

This generates the unharvested control strategy. It then plots the size spectrum, feeding level vs size, mortality vs size, biomass vs time, and reproduction.

```{r unharvested simulation, message=FALSE, warning=FALSE}
# Trait-based model parameters
params <- newTraitParams(no_sp = 9)

# Experimental variables
S.list <- rep(.01, 3)
F.list <- rep(0, 3)
  
gear_params(params) <- data.frame(species = species_params(params)$species,
                                  gear = c(rep("small", 3), rep("medium", 3), rep("large", 3)),
                                  sel_func = "knife_edge",
                                  sel = rep(S.list, each = 3),
                                  knife_edge_size = species_params(params)$w_inf * rep(S.list, each = 3))

# Simulation run
sim0 <- project(params, t_max = 300, effort = c("small" = F.list[1],
                                                "medium" = F.list[2],
                                                "large" = F.list[3]))
plot(sim0)
```

## Unharvested Metrics

We will save the unharvested metrics for comparison to the experimental strategies. For details, see `metrics.R`.

```{r unharvested metrics}
metrics0 <- unharvestedMetrics(sim0)
metrics_full <- metrics0[, -24:-33]
```

## Simulation Loop

Now we will loop through randomized strategies that are compared to the metrics of the unharvested strategy `metrics0`. This will compute `counter` strategies that will be assigned a unique `stratID` starting from wherever `strategies_df` left off.

```{r simulation loop, message=FALSE, warning=FALSE}
counter <- 2
strat.start <- max(strategies_df$stratID)

metrics_full_init <- matrix(0,
                            nrow = counter,
                            ncol = length(metrics_full))
metrics_full <- rbind(metrics_full, metrics_full_init)

for (count in 2:(1+counter))
{
  strat <- strat.start + count - 1
  # Experimental variables
  F.list <- runif(3, 0, 3)
  S.list <- runif(3, 0, 1)

  # Trait-based model parameters
  gear_params(params)$sel <- rep(S.list, each = 3)
  gear_params(params)$knife_edge_size <- species_params(params)$w_inf * gear_params(params)$sel

  # Simulation run
  sim1 <- project(params, t_max = 300, effort = c("small" = F.list[1],
                                                  "medium" = F.list[2],
                                                  "large" = F.list[3]))
  
  # Add metrics
  metrics_full[count,] <- strategyMetrics(sim1, strat, metrics0)
  fprintf("%d, %d\n", count, strat)
}
```

To write to the csv file, we convert the matrix to a dataframe. We then append it to the `strategies_df` so we can add more in the future.

```{r convert metrics to dataframe}
metrics_df <- as.data.frame(metrics_full[-1,])
strategies_df <- bind_rows(strategies_df, metrics_df)
```

```{r strategies table, echo=FALSE}
knitr::kable(head(strategies_df))
```


```{r write to csv, eval=FALSE, include=FALSE}
write.csv(strategies_df,
          file.path(here(), 'data',
                    'fishcarbon_metrics.csv'),
          row.names = FALSE)
```


$~$
# Plots

```{r biomass vs yield plot}
ggplot(strategies_df, aes(x=Y, y=B, color=Wmean )) +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dotted") +
  ggtitle("Average annual yield versus average annual biomass at equilibrium") +
  ylab("Average annual biomass (g)") + xlab("Average annual yield (g)") +
  scale_color_gradient(low = "blue", high = "red")
```

```{r correlation, message=FALSE}
library(corrplot)
M = cor(strategies_df)
testRes = cor.mtest(strategies_df, conf.level = 0.95)
corrplot(M, method = 'square', type = 'lower', p.mat = testRes$p, sig.level = 0.10)
```

